Load the libraries 
```{r,warning=FALSE}
library(Seurat)
library(ggplot2)
library(CellChat)
library(SingleR)
library(data.table)
library(celldex)
library(pathfindR)
library(future)
library(ggalluvial)
library(clusterProfiler)
library(org.Hs.eg.db)
library(VennDiagram)
library(ggvenn)
library(RColorBrewer)
```

load the objects
```{r}
load('r_objects/whole_integration_obj.Rdata')
load('r_objects/marker_list.Rdata')
load("r_objects/hcc_deg.Rdata")
load("r_objects/icc_deg.Rdata")
```
Preprocessing was performed before Integration, "whole_integration_obj.Rdata" 
Name of the integrated object 
Step1. Visualisation of Major features in the integrated ObjectI
```{r}
integration_obj[['Percent_Mito_genes']]  <- PercentageFeatureSet(integration_obj,pattern = "^MT-",assay = "RNA")
integration_obj[['Percent_ribosomal_protein_genes']] = PercentageFeatureSet(integration_obj,pattern = "^RP[SL]",assay = "RNA") 
#only consider those cells having mitochondial genes less than 50 percent
valid_mito_genes <- WhichCells(integration_obj,expression = Percent_Mito_genes < 50 )
integration_obj <-  subset(integration_obj,cells = valid_mito_genes)
violin_plot <- VlnPlot(integration_obj,
                       features =c('Percent_Mito_genes',"nCount_RNA","nFeature_RNA",'Percent_ribosomal_protein_genes'),
                       pt.size = FALSE, group.by = "sample_type")

```
Step. High variance gene identification, dimension reduction and clustering
```{r}
integration_obj <-FindVariableFeatures(integration_obj,nfeatures = 4000, selection.method = "vst")
integration_obj <- Seurat::ScaleData(integration_obj)
integration_obj <- Seurat::RunPCA(integration_obj,features = VariableFeatures(integration_obj))
integration_obj <-  FindNeighbors(integration_obj,dims = 1:50)
integration_obj <- FindClusters(integration_obj)
```
Visualisation 
```{r}
umap_sample_type <- DimPlot(integration_obj,reduction = 'umap',group.by = 'sample_type')
umap_seu_clust <- DimPlot(integration_obj,reduction = 'umap',group.by = 'seurat_clusters')
tsne_sample_type <- DimPlot(integration_obj,reduction = 'tsne',group.by = 'sample_type')
tsne_seu_clust <- DimPlot(integration_obj,reduction = 'tsne',group.by = 'seurat_clusters',label = T)
```
celltype annotation 
```{r}
DefaultAssay(integration_obj)="RNA"
ref <- HumanPrimaryCellAtlasData()
single_cell_exp <- as.SingleCellExperiment(integration_obj)
integration_obj <- SetIdent(integration_obj, value = integration_obj@meta.data$seurat_clusters )
single_r_prediction <- SingleR::SingleR(test = single_cell_exp,
                                        ref = ref,
                                        clusters =Idents(integration_obj)  ,
                                        labels = ref$label.main)
single_r_prediction <- as.data.frame(single_r_prediction)
```
Finding marker genes for cell clusters and Cell-annotation
```{r}
Idents(integration_obj) <-  integration_obj$cell_type
cell_type_labels <- unique(integration_obj$cell_type)
marker_list<- list()
for (celltype in cell_type_labels) {
  temp_mark <- FindMarkers(integration_obj,ident.1 = celltype,min.pct=0.25,min.diff.pct = 0)
  marker_list[[celltype]] <- temp_mark
}
save(marker_list,file='R_objects/marker_list.Rdata')

#Heatmap of DEGS
no_of_celltypes <- length(marker_list)
marker_gene_clusters <- data.frame(matrix(nrow = no_of_celltypes,ncol = 21))
colnames(marker_gene_clusters) <- c('Celltype')
#marker_gene_clusters$cell_types <- single_r_prediction$labels
for(num in 1:no_of_celltypes ){
  ct <- cell_type_labels[num]
  temp_marker <- marker_list[[ct]]
  marker_gene_clusters[num,1] <- ct
  marker_gene_df <- head(temp_marker[sort(temp_marker$avg_log2FC,decreasing = T,index.return=T)$ix,],20)
  marker_gene_clusters[num,2:21] <- rownames(marker_gene_df)
}

```
Differential gene expression analysis
```{r}
hcc_deg <- hcc_deg[abs(hcc_deg$avg_log2FC)> 2.0,]
icc_deg <- icc_deg[abs(icc_deg$avg_log2FC)> 2.0,]
```
Cell cell communication analysis
```{r}
#.......Cell chat object creation
cell_chat_obj <-  CellChat::createCellChat(object = integration_obj,
                                             group.by = 'cell_type',assay = 'RNA')

#.......call cell chat database
cell_chat_db = CellChatDB.human
dbs_in_cellchat <- showDatabaseCategory(cell_chat_db)   #what signaling datas are there 
#Select the database 
cell_chat_db.use <- subsetDB(cell_chat_db,
                             search = "Secreted Signaling")
#cell_chat_db.use <- subsetDB(cell_chat_db)
#integrate database to our cell chat object
cell_chat_obj@DB <- CellChatDB.human

#.......Downstream cell chat analysis 
cell_chat_obj <- subsetData(cell_chat_obj)
cell_chat_obj <- identifyOverExpressedGenes(cell_chat_obj)
cell_chat_obj <- identifyOverExpressedInteractions(cell_chat_obj)
cell_chat_obj <- projectData(cell_chat_obj,PPI.human)
#Compute communication probability of  between cells of clusters 
cell_chat_obj <- computeCommunProb(cell_chat_obj)   #What are the pathways present 
cell_chat_obj <- filterCommunication(cell_chat_obj,min.cells = 10)

df.net <- subsetCommunication(cell_chat_obj)

#compute probability of pathways
cell_chat_obj <- computeCommunProbPathway(cell_chat_obj)

#After calculating communication networks gonna aggregate(sum) it 
cell_chat_obj <- aggregateNet(cell_chat_obj)
interaction_dfs <- cell_chat_obj@net

#...............plot the interactions 
group_size <- as.numeric(table(cell_chat_obj@idents))

#...............plot1.No of interactions
interaction_plot <- netVisual_circle(cell_chat_obj@net$count,
                                     vertex.weight = group_size,
                                     weight.scale = T,
                                     label.edge = F)
```
Gene enrichment Analysis 
```{r}
#HCC.........................................................................
hcc_deg_up <- hcc_deg[hcc_deg$avg_log2FC>1.5,]
hcc_up_regulated <- data.frame(rownames(hcc_deg_up),hcc_deg_up$avg_log2FC,hcc_deg_up$p_val)
colnames(hcc_up_regulated) <- c("Gene.symbol","logFC","adj.P.Val")
hcc_up_df <- run_pathfindR(hcc_up_regulated, iterations = 5, n_processes = 2)
hcc_up_gse <- enrichGO(hcc_up_regulated$Gene.symbol, 
             ont ="CC", 
             keyType = "SYMBOL",OrgDb = 'org.Hs.eg.db')
hcc_up_chart <- enrichment_chart(hcc_up_df,top_terms = 10)
hcc_up_chart <- barplot(hcc_up_gse,drop=T,showCategory = 10)+ggtitle("HCC up regulated")
hcc_deg_down <- hcc_deg[hcc_deg$avg_log2FC<(-1.5),]
hcc_down_regulated <- data.frame(rownames(hcc_deg_down),hcc_deg_down$avg_log2FC,hcc_deg_down$p_val)
colnames(hcc_down_regulated) <- c("Gene.symbol","logFC","adj.P.Val")
hcc_down_gse <- enrichGO(hcc_down_regulated$Gene.symbol, 
             ont ="CC", 
             keyType = "SYMBOL",OrgDb = 'org.Hs.eg.db')
hcc_down_chart <- barplot(hcc_down_gse,drop=T,showCategory = 10)+ggtitle("HCC down regulated")
#ICC........................................................................
#up_regulate
icc_deg_up <- icc_deg[icc_deg$avg_log2FC>2,]
icc_up_regulated <- data.frame(rownames(icc_deg_up),icc_deg_up$avg_log2FC,icc_deg_up$p_val)
colnames(icc_up_regulated) <- c("Gene.symbol","logFC","adj.P.Val")
icc_up_gse <- enrichGO(icc_up_regulated$Gene.symbol, 
             ont ="CC", 
             keyType = "SYMBOL",OrgDb = 'org.Hs.eg.db')
icc_up_chart <- barplot(icc_up_gse,drop=T,showCategory = 10)+ggtitle("ICC up regulated")
#down_regulate
icc_deg_down <- icc_deg[icc_deg$avg_log2FC<(-2),]
icc_down_regulated <- data.frame(rownames(icc_deg_down),icc_deg_down$avg_log2FC,icc_deg_down$p_val)
colnames(icc_down_regulated) <- c("Gene.symbol","logFC","adj.P.Val")
icc_down_gse <- enrichGO(icc_down_regulated$Gene.symbol, 
             ont ="CC", 
             keyType = "SYMBOL",OrgDb = 'org.Hs.eg.db')
icc_down_chart <- barplot(icc_down_gse,drop=T,showCategory = 10)+ggtitle("ICC down regulated")
```
Thank you

